\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
comment outlined at top of file detailing annoying style checklist
time-consuming, error-prone, AN error not A error

% Python           "Python" everywhere
% part features   emph'd on first use
% part assembly   emph'd on first use
% physical volume  emph'd on first use
% logical volume  emph'd on first use
% daughter volume emph'd on first use
% mother volume   emph'd on first use
% Reader     emph'd on first use
% scene      emph not on first use, but first novel/unconventional use.
% API        paren on first use
% AST        paren on first use
% BREP (not B-REP)  BREP everywhere
% region    emph'd on first use
% zone      emph'd on first use
% subzone   emph'd on first use

@@

\begin{abstract}
Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is a 
error prone and time consuming task. Simulating a system often requires geometry from different sources and modelling 
environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 
that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 
geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with small  
examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
extensions and future work.
\end{abstract}

>>>>

% STYLE AND OTHER ANNOYING STUFF:

%%%% HYPHENATION:
% Python           "Python" everywhere
% BREP (not B-REP)  BREP everywhere

%%%% EMPH
% part features   emph'd on first use
% part assembly   emph'd on first use
% physical volume  emph'd on first use
% logical volume  emph'd on first use
% daughter volume emph'd on first use
% mother volume   emph'd on first use
% Reader     emph'd on first use
% scene      emph not on first use, but first novel/unconventional use.
% API        paren on first use
% AST        paren on first use
% region    emph'd on first use
% zone      emph'd on first use
% subzone   emph'd on first use

%% TYPEWRITER /

@@

\begin{abstract}
Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is an
error-prone and time-consuming task. Simulating a system often requires geometry from different sources and modelling 
environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 
that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 
geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with small  
examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
extensions and future work.
\end{abstract}
